Determining Bravais Lattice Types

### 2025-07-02 SELLA/Sella.tex
Web_URL -- updated CmdLM to CmdLMS6 and added CmdLMP3
Sella -- added the critique that Claude wrote.

@@

	\citeasnoun{Zimmermann1985} described the program, DELOS
	for the same purpose and based on the use of Selling scalars, which
	SELLA uses as well; they treat the scalars as a list of 6 numbers, but do not consider them as points in 
	a space.  SELLA treats the scalars as elements of vectors in the 6-dimensional
	space, \SVI. Treating lattices as points in a liner space accesses the tools
	and systematic procedures of linear algebra.

	\citeasnoun{andrews2014} reviewed the literature on 
	 efforts to create methods to utilize data that contain unavoidable 
	measurement error and adds a more generic view of the problem.

@@

	\citeasnoun{Delaunay1932} found that the 14 Bravais lattice types 
	could be allocated among 24 types that are determined by the 
	type of Dirichlet unit cell (termed the Voronoi region \cite{Voronoi1908} or 
	Dirichlet region \cite{dirichlet1850} by 
	Delone). Delone used the convention of \citeasnoun{Bravais1850}
	using the sides of the tetrahedron labeled by the symbols of the six
	Selling scalars. Figure \ref{fig:PQRSTU} shows the labeling used in
	the International Tables for Crystallography \cite{Henry1952}; 
	Table \ref{table:ScalarConcordance} shows other choices that have been used. The
	contents for each type are described in Figure \ref{fig:PQRSTU}.

	\citeasnoun{Burzlaff1985} revised the labeling of the types.
	Here we have returned to the numbering of the Bravais types to that 
	of \citeasnoun{Delaunay1932}.
	In some cases, Delone included two forms within a single 
	type. \citeasnoun{Burzlaff1985}
	renumbered by ordinals. We have labeled the Delone 
	types that have multiple items as "A" and "B". Table \ref{table:DeloneTypeConcordance}
	shows the various labelings. Figure \ref{fig:rotatedDeloneTypes} 
	revises the figure of \citeasnoun{Delaunay1932}, using 
	more modern notation. Table \ref{table:ScalarConcordance} 
	lists the various labelings that have been 
	used for the sides of the Bravais tetrahedron. 
	Figure \ref{fig:PQRSTU} shows the arrangement of the 
	symbols as used in the International Tables for Crystallography.

@@

	\begin{table}
		\begin{tabular}{ccccccccc}
			\toprule
			\cite{Delaunay1932} & \cite{Burzlaff1985}   &this  \\
			&  & paper \\
			\midrule
			K$_I$ & K1 & C1 & cI \\		
			K$_{III}$ & K2 & C3 &cF \\		
			K$_V$ & K3 & C5 &cP \\		
			Q$_I$ & Q1 & T1 &tI \\		
			Q$_{II}$ & Q2 & T2 &tI \\		
			Q$_V$ & Q3 & T5 & tP\\		
			R$_I$ & R1 & H1 & hR \\		
			R$_{III}$ & R2 & H3 & hR \\		
			O$_I$ & O1 & O1A & oF  \\		
			O$_I$ & O2 & O1B &oI  \\		
			O$_{II}$ & O3 & O2 & oI   \\		
			O$_{III}$ & O4 & O3$^*$ & oI   \\		
			O$_{IV}$ & O5 & O4 & oS   \\		
			O$_V$ & O6 & O5 & oP   \\		
			M$_I$ & M1 & M1A & mC  \\		
			M$_I$ & M2 & M1B & mC \\		
			M$_{II_2}$  & M3 & M2A$^*$ & mC \\		
			M$_{II}$ & M4 & M2B$^*$ & mC  \\		
			M$_{III}$ & M5 & M3 & mC  \\		
			M$_{IV}$ & M6 & M4 & mP  \\		
			T$_I$ & T1 & A1 & aP  \\ 		
			T$_{II}$ & T2 & A2$^*$ & aP \\		
			T$_{III}$ & T3 & A3$^*$ & aP \\		
			H$_{IV}$  & H1 & H4 & hP \\ 
			\bottomrule
		\end{tabular}
		~\\ ~\\
		\caption{The 24 Delone types. \cite{Delaunay1932}\\
			$^*$ not a full Bravais type.}
		\label{table:DeloneTypeConcordance}
	\end{table}

	\subsection{The space \SVI{}}
	\cite{andrews2019} recast the Selling parameters to define a metric space, \SVI{}.
	The base vectors, $\bf{a}$, $\bf{b}$, $\bf{c}$ of the unit cell
	are used to define $\bf{d}=-(\bf{a}+\bf{b}+\bf{c})$.
	A point ${s}$ in \SVI{} is defined as:\\
	${s}$= [\scalarsub{s}{1}, \scalarsub{s}{2}, \scalarsub{s}{3},\scalarsub{s}{4}, \scalarsub{s}{5}, \scalarsub{s}{6}] \\
	where \scalarsub{s}{1}=\vdotv{b}{c}, ~\scalarsub{s}{2}=\vdotv{a}{c}, ~\scalarsub{s}{3}=\vdotv{a}{b}, 
	~\scalarsub{s}{4}=\vdotv{a}{d}, ~\scalarsub{s}{5}= \vdotv{b}{d}, and \scalarsub{s}{6}=\vdotv{c}{d}.

@@

	\subsection{Character}
	In \SVI{} for reduced cells, each Bravais type is a single, connected,
	origin-inclusive, Euclidean manifold. As such, all points in a
	particular manifold can be described by their ``character'', 
	a representation of the vectorsns of that type. The table of \citeasnoun{Delaunay1932} included this information 
	encoded in the formalism of Bravais, as a tetrahedron, with
	the sides marked to show which of the 6 Selling parameters were
	zero or which pairs (or multiplets) have equal values.

@@

	We will need to create projectors for each of the Bravais
	lattice types. The projectors will be use to generate
	images of probe points in each of the types, and the perps
	will measure the distance from each manifold.

	We will use Selling reduction; Niggli reduction has a fundamental 
	unit that is non-convex and some boundaries of the fundamental 
	unit are partly closed and partly open \cite{andrews2014} leading 
	to considerable complexity. Because Niggli reduction divides the 
	fundamental unit of Niggli reduction into separate all obtuse and all acute regions, 
	the transitions between those are quite complex \cite{andrews2014}. 
	In space \SVI{} \cite{andrews2019b}, the fundamental 
	unit is the simple all-negative orthant of a 6-dimensional 
	Cartesian space. Only two kinds of operations in the space 
	will need to be considered: the 6  transform operations 
	at the boundaries of the orthant (zeros of an axis) and 
	24 reflections (allowed permutations) \cite{andrews2019}

	Twenty-four lattice types were enumerated by \citeasnoun{Delaunay1932}. 
	Three of those are triclinic, and we will ignore them because all crystals 
	can be indexed as triclinic. We 
	shall need all representations of all non-triclinic lattice 
	types within the \SVI{} fundamental unit (all Selling-reduced 
	cells) or those generated beyond the boundaries by boundary transforms. 
	Three forms (M3, M2B, and O3) are reduced dimension boundaries that do
	not correspond to unique Bravais types; any lattice that falls in those
	three is indexed by one of the other types.

	Seven of the 21 Delone types do not have a zero in their \SVI{} 
	representation; the presence of zero indicates that a form is 
	on the boundary of the \SVI{} fundamental unit. Since a 
	point on the boundary transforms to another boundary 
	point \cite{andrews2019b}, we can generate the Virtual 
	Cartesian Point (VCP) \cite{andrews2019b} appropriate to 
	each zero in the \SVI{} vector. Because the reduction
	operations do not commute, in the cases where there is more 
	than one zero in the vector, all orderings of applying 
	reductions to all of the zeros must be generated. (For example, 
	for two zeros, there will be six vectors produced.) Again, 
	there may be many duplicate results.

	Finally, the projectors must be computed for each of the many 
	sample vectors of the 21 types. We will also need the 
	``perps'', the operators that give the normal vector to each 
	such manifold. For a particular manifold, the projector 
	applied to the probe gives
	the least-squares best fit point within that manifold
	to the probe vector. 
	Perps are computed by subtracting the 
	corresponding projector from the unit matrix. The norm of avector
	created by multiplying the probe times the projector
	 is the distance from that manifold.

@@

	Step 1: Generate any random vector that contains no zero 
	values and no duplicate values.  For a later operation, 
	it should only contain values large enough that adding or
	subtracting the smallest
	representable floating point number will not change the 
	value in computer arithmetic ($DBL\_MIN$ in the C language).
	That value will be used to mark the positions of zeros
	in vectors that have been processed.

	Step 2; For each Delone type, multiply its projector times 
	the vector from Step 1. Store  the resulting vector
	from Step 1 in a list 
	with entries for each Bravais type (see Table \ref{table:DeloneTypes} 
	for the projectors).

	Step 3:

	a) If the vector result of Step 2 contains no zeros, generate the 24 reflections
	and store in the list by Bravais type.

	\textit{\textbf{LCA--need to normalize the vectors, just like 
		in lattice matching. ? Can we use the 
		lattice matching code here? This is very 
		incomplete. The processing of multiple zeros is MISSING! But the use of DBL\_MIN is there.}}

@@

	Consider the case of M4, primitive monoclinic, the character is \charseq{00r stu}. 
	For particular values for r,s,t,u, the best monoclinic cell will not
	depend on whatever values are substituted for the zeros. (It does not depend on the zero values because the projectors to that 
	manifold create zero elements for any vector.) Imangine a plane
	with axis that are the values of the two elements of the character that are zero. Points in the plane represent unit 
	cells with angles defined by the \scalarsub{s}{1} and \scalarsub{s}{2} and r,s,t,u. We can draw a circle in the
	\scalarsub{s}{1},\scalarsub{s}{2} plane, each point
	on the circle corresponding to a lattice.

@@

	Bravais type O4 (side-centered orthorhombic) has two zeros and a pair of required equal values, 
character \charseq{00r~sst}. The zeros can be treated the same as above
for the case of M4 (primitive monoclinic). 
	The pair of equal values must 
	have an average value that remains equal to $\bf{s}$ in the lattice character. 
	That means 3 values to vary (the 2 zeros and the distance fomaverage
	value for the equal scalars), and we can create a sphere around 
	the point \charseq{00r~sst}. See Figure \ref{fig:O4}.

	\section{Comparisons}
	\textit{\textbf{LCA this section is incomplete. Table needs caption/label.}}
	Comparison to other distance measure; Data for other measures taken
	from \citeasnoun{andrews2014}.

\begin{table}
	\begin{tabular}{cccccc}
		\toprule
		Lattice character & \GVI{} distance & BGAOL Z score & XDS QI & Scaled QI & Sella \\
		\midrule
		mP               &     20.138  & 0.657    &   1.0  & 0.13  & 1.06\\	
		oC               &     125.958 &  3.560   &    23. & 8 3.09& 13.82\\	
		mC               &     125.150 &  4.085   &    23. & 4 3.03& 13.80\\	
		\bottomrule
	\end{tabular}
	\caption{Comparison of distance measures}
	\label{tab:comparisons}
\end{table}
	~\\

@@

	\begin{figure}
		\label{fig:M4}
		\caption{Delone type M4: there are two zeros. A circle of 100 points with
			radius 0.1 is centered at 0,0. The lattices are reduced and the points are
			plotted at the distance from M4.} The red points indicate the original
		circle. The blue points are for the reduced cells.
		\includegraphics[width=12cm]{M4-100-2-zeros}
	\end{figure}

@@

	\begin{figure}
		\caption{Delone type O4: There are two zeros and one pair.
			A sphere with radius 0.1 was placed around one point. At each
			sphere point, the lattice was reduced and the point on the sphere
			was assigned a color (0.01) to blue (0.0075). 100,000 points are plotted.}
		\label{fig:O4}
		\includegraphics[width=12cm]{O4_Cropped-2-zeros-1-pair}
	\end{figure}

>>>>

%	Claude.ai suggestions 10125-04-13
%	I've reviewed your paper on Bravais lattice determination using the SELLA algorithm, and I have several suggestions for improvements:
%	
%	Consistency in terminology: There are variations between "Delaunay" and "Delone" throughout the paper. While you note that Delaunay later changed his name's spelling, consistency within the paper would be helpful. Perhaps use one version with a note about the alternative spelling at first mention.
%	Incomplete sections: Several sections are marked as incomplete:
%	
%	Section 3.1.1 has a note "LCA–need to normalize the vectors..."
%	Section 3.1.2 has "LCA write pseudocode for Fraction."
%	Section 6 "LCA this section is incomplete. Table needs caption/label."
%	Sections 7 and 8 are just headings without content.
%	
%	
%	Figure numbering: There appear to be duplicate Figure 1 entries - one on page 15 and another on page 16, both showing the Bravais tetrahedron.
%	Table numbering: Table 4 appears without a proper caption on page 13.
%	Equation formatting: Many mathematical expressions could benefit from proper equation formatting, particularly in the algorithm descriptions.
%	References: Some references in the text don't match entries in the reference list, and some citations don't follow a consistent format.
%	Structural organization: The paper would benefit from clearer delineation between the theoretical foundations and the practical algorithm implementation.
%	Typographical errors: Several minor typographical issues:
%	
%	"Imangine a plane" instead of "Imagine a plane" (page 12)
%	"the distance fomaverage value" instead of "from average value" (page 12)
%	"LCA," notes to self should be removed for publication
%	
%	
%	Technical clarity: The step-by-step description of the algorithm in Section 3 could be improved with clearer pseudocode or examples.
%	Figure descriptions: Figures 5-7 need more detailed captions explaining what is being visualized and how to interpret the colored points.
%	
%	I hope these suggestions are helpful for improving your manuscript.

@@

	\citeasnoun{Zimmermann1985} described the program, DELOS
	for the above purpose and based on the use of Selling scalars, which
	SELLA uses as well; they treat the scalars as a list of 6 numbers, but do not consider them as points in 
	a space.  SELLA treats the scalars as elements of vectors in the 6-dimensional
	space, \SVI. Treating lattices as points in a liner space accesses the tools
	and systematic procedures of linear algebra.

	\citeasnoun{andrews2014} reviewed the literature on 
	 efforts to create methods to utilize data that contain unavoidable 
	measurement error, and they add a more generic view of the problem.

@@

	\citeasnoun{Delaunay1932} found that the 14 Bravais lattice types 
	could be allocated among 24 types (here termed "Delone Types") that are determined by the 
	type of Dirichlet unit cell (termed the Voronoi region \cite{Voronoi1908} or 
	Dirichlet region \cite{dirichlet1850} by 
	Delone). Delone used the tetrahedral convention of \citeasnoun{Bravais1850}
	using the sides of the tetrahedron labeled by the symbols of the six
	Selling scalars. Figure \ref{fig:PQRSTU} shows the labeling used in
	the International Tables for Crystallography \cite{Henry1952}; 
	Table \ref{table:ScalarConcordance} shows other choices that have been used. The
	contents for each type are described in Figure \ref{fig:PQRSTU}.

	\citeasnoun{Burzlaff1985} revised the labeling of the types.
	Here we have returned to the numbering of the Bravais types to that 
	of \citeasnoun{Delaunay1932}, which addresses the type
	of Federov polyhedron for the reduced cell.
	In some cases, Delone included two forms within a single 
	type. \citeasnoun{Burzlaff1985}
	renumbered by ordinals. We have labeled the Delone 
	types that have multiple items as "A" and "B". Table \ref{table:DeloneTypeConcordance}
	shows the various labelings. Figure \ref{fig:rotatedDeloneTypes} 
	revises the figure of \citeasnoun{Delaunay1932}, using 
	more modern notation. Table \ref{table:ScalarConcordance} 
	lists the various labelings that have been 
	used for the sides of the Bravais tetrahedron. 
	Figure \ref{fig:PQRSTU} shows the arrangement of the 
	symbols as used in the International Tables for Crystallography.

@@

	\begin{table}
		\begin{tabular}{ccccccccc}
			\toprule
			\cite{Delaunay1932} & \cite{Burzlaff1985}   &this &Pearson  \\
			&  & paper & symbol\\
			\midrule
			K$_I$ & K1 & C1 & cI \\		
			K$_{III}$ & K2 & C3 &cF \\		
			K$_V$ & K3 & C5 &cP \\		
			Q$_I$ & Q1 & T1 &tI \\		
			Q$_{II}$ & Q2 & T2 &tI \\		
			Q$_V$ & Q3 & T5 & tP\\		
			R$_I$ & R1 & H1 & hR \\		
			R$_{III}$ & R2 & H3 & hR \\		
			O$_I$ & O1 & O1A & oF  \\		
			O$_I$ & O2 & O1B &oI  \\		
			O$_{II}$ & O3 & O2 & oI   \\		
			O$_{III}$ & O4 & O3$^*$ & oI   \\		
			O$_{IV}$ & O5 & O4 & oS   \\		
			O$_V$ & O6 & O5 & oP   \\		
			M$_I$ & M1 & M1A & mC  \\		
			M$_I$ & M2 & M1B & mC \\		
			M$_{II_2}$  & M3 & M2A$^*$ & mC \\		
			M$_{II}$ & M4 & M2B$^*$ & mC  \\		
			M$_{III}$ & M5 & M3 & mC  \\		
			M$_{IV}$ & M6 & M4 & mP  \\		
			T$_I$ & T1 & A1 & aP  \\ 		
			T$_{II}$ & T2 & A2$^*$ & aP \\		
			T$_{III}$ & T3 & A3$^*$ & aP \\		
			H$_{IV}$  & H1 & H4 & hP \\ 
			\bottomrule
		\end{tabular}
		~\\ ~\\
		\caption{The 24 Delone types. \cite{Delaunay1932}\\
			$^*$ not a full Bravais type.}
		\label{table:DeloneTypeConcordance}
	\end{table}

	\subsection{The space \SVI{}}
	\citeasnoun{andrews2019} recast the Selling parameters as a metric space, \SVI{}.
	The base vectors, $\bf{a}$, $\bf{b}$, $\bf{c}$ of the unit cell
	are used to define $\bf{d}=-(\bf{a}+\bf{b}+\bf{c})$.
	A point ${s}$ in \SVI{} is defined as:\\
	${s}$= [\scalarsub{s}{1}, \scalarsub{s}{2}, \scalarsub{s}{3},\scalarsub{s}{4}, \scalarsub{s}{5}, \scalarsub{s}{6}] \\
	where \scalarsub{s}{1}=\vdotv{b}{c}, ~\scalarsub{s}{2}=\vdotv{a}{c}, ~\scalarsub{s}{3}=\vdotv{a}{b}, 
	~\scalarsub{s}{4}=\vdotv{a}{d}, ~\scalarsub{s}{5}= \vdotv{b}{d}, and \scalarsub{s}{6}=\vdotv{c}{d}.

@@

	\subsection{Character}
	In \SVI{} for reduced cells, each Bravais type is a single, connected,
	origin-inclusive, Euclidean manifold. As such, all points in a
	particular manifold can be described by their ``character'', 
	a representation of the vectors of that type. The table of \citeasnoun{Delaunay1932} included this information 
	encoded in the formalism of Bravais, as a tetrahedron, with
	the sides marked to show which of the 6 Selling parameters were
	zero or which pairs (or multiplets) have equal values.

@@

	Sella creates projectors for each of the Bravais
	lattice types. The projectors will be used to generate
	images of probe points in each of the types, and the perps
	will measure the distance from each manifold. Perps
	are the matrices that when multiplied times a vector,
	create a vector that is the component of the input 
	that is orthogonal to the domain that the projector
	is associated with.

	We will use Selling reduction; Niggli reduction has a reduced
	domain that is non-convex and some boundaries of the 
	reduced domain are partly closed and partly open \cite{andrews2014} leading 
	to considerable complexity. Because Niggli reduction divides the 
	fundamental unit of Niggli reduction into separate all obtuse and all acute regions, 
	the transitions between those are quite complex \cite{andrews2014}. 
	In space \SVI{} \cite{andrews2019b}, the reduced domain is the simple, convex all-negative orthant of a 6-dimensional 
	Cartesian space. Only two kinds of operations in the space 
	will need to be considered: the transform operations 
	at the boundaries of the reduced orthant (zeros of an axis) and 
	24 reflections (allowed permutations) \cite{andrews2019}

	Twenty-four lattice types were enumerated by \citeasnoun{Delaunay1932}. 
	Three of those are triclinic, and we will ignore them because all crystals 
	can be indexed as triclinic. We 
	shall need all representations of all non-triclinic lattice 
	types within the \SVI{} fundamental unit (all Selling-reduced 
	cells) or those generated beyond the boundaries by boundary transforms. 
	Three forms (M3, M2B, and O3) are reduced-dimension boundaries between 2 Delone Types, that do
	not correspond to unique Bravais types; any lattice that falls in those
	three is indexed by both of the other types.

	Seven of the 19 non-triclinic, nondegenerate Delone types do not have a zero in their \SVI{} 
	representation; the presence of zero indicates that a form is 
	on the boundary of the \SVI{} fundamental unit. Since a 
	point on the boundary transforms to another boundary 
	point \cite{andrews2019b}, we can generate the Virtual 
	Cartesian Point (VCP) \cite{andrews2019b} appropriate to 
	each zero in the \SVI{} vector. Because the reduction
	operations do not commute, in the cases where there is more 
	than one zero in the vector, all orderings of applying 
	reductions to all of the zeros must be generated. (For example, 
	for two zeros, there will be six vectors produced.) Again, 
	there may be many duplicate results.

	Finally, the projectors must be computed for each of the many 
	sample vectors of the 21 types. We will also need the 
	``perps'', the operators that give the normal vector to each 
	such manifold. For a particular manifold, its projector 
	applied to the probe gives
	the least-squares best fit point within that manifold
	to the probe vector. 
	Perps are computed by subtracting the 
	corresponding projector from the unit matrix. The norm of a vector
	created by multiplying the probe times a projector
	 is the distance from that manifold.

@@

	For each Delone Type, we will create a list of
	vectors that can be generated for that type.

	\emph{Step 1:}

	Generate any random vector that contains no zero 
	values and no duplicate values.  For a later operation, 
	it should only contain values large enough that adding or
	subtracting the smallest
	representable floating point number will not change the 
	value in computer arithmetic ($DBL\_MIN$ in the C language).
	That value will be used to mark the positions of zeros
	in vectors that have been processed.

	\emph{Step 2:}

	 For each Delone type, multiply its projector times 
	the vector from Step 1. Store  the resulting vector
	from Step 1 in a list 
	with entries for each Delone type (see Table \ref{table:DeloneTypes} 
	for the projectors).

	\emph{Step 3:}

	a) If the vector result of Step 2 contains no zeros, generate the 24 reflections
	and store in the list by Delone type.

@@

	Consider the case of M4, primitive monoclinic, the character is \charseq{00r stu}. 
	For particular values for r,s,t,u, the best monoclinic cell will not
	depend on whatever values are substituted for the zeros. (It does not depend on the zero values because the projectors to that 
	manifold create zero elements for any vector.) Imagine a plane
	with axis that are the values of the two elements of the character that are zero. Points in the plane represent unit 
	cells with angles defined by the \scalarsub{s}{1} and \scalarsub{s}{2} and r,s,t,u. We can draw a circle in the
	\scalarsub{s}{1},\scalarsub{s}{2} plane, each point
	on the circle corresponding to a lattice.

@@

	Bravais type O4 (side-centered orthorhombic) has two zeros and a pair of required equal values, 
character \charseq{00r~sst}. The zeros can be treated the same as above
for the case of M4 (primitive monoclinic). 
	The pair of equal values must 
	have an average value that remains equal to $\bf{s}$ in the lattice character. 
	That means 3 values to vary (the 2 zeros and the distance from average
	value for the equal scalars), and we can create a sphere around 
	the point \charseq{00r~sst}. See Figure \ref{fig:O4}.

	\section{Comparisons}
	\textit{\textbf{LCA this section is incomplete. Table needs caption/label.}}

\begin{table}
	\begin{tabular}{cccccc}
		\toprule
		Lattice character & \GVI{} distance & BGAOL Z score & XDS QI & Scaled QI & Sella \\
		\midrule
		mP               &     20.138  & 0.657    &   1.0  & 0.13  & 1.06\\	
		oC               &     125.958 &  3.560   &    23. & 8 3.09& 13.82\\	
		mC               &     125.150 &  4.085   &    23. & 4 3.03& 13.80\\	
		\bottomrule
	\end{tabular}
	\caption{Comparison to other distance measure; Data for other measures taken from \citeasnoun{andrews2014}.}
	\label{tab:comparisons}
\end{table}
	~\\

@@

	\begin{figure}
		\label{fig:M4}
		\caption{Delone type M4: there are two zeros. A circle of 100 points with
			radius 0.1 is centered at 0,0. The lattices are reduced and the points are
			plotted at the distance from M4. The red points indicate the original
		circle. The blue points are for the reduced cells.}
		\includegraphics[width=12cm]{M4-100-2-zeros}
	\end{figure}

@@

	\begin{figure}
		\caption{Delone type O4 (character \charseq{00r stu}): There are two zeros and one pair.			 
			100,000 points are plotted; for each
			 point, the corresponding lattice was reduced; each point
			is assigned a color (0.01) to blue (0.0075),
			according to its reduced distance from the origin.}
		\label{fig:O4}
		\includegraphics[width=12cm]{O4_Cropped-2-zeros-1-pair}
	\end{figure}
